Assignment 4

### 2015-03-10 rmtw/a4/latex8.tex
sdfsa

\SubSection{Tests Used for H\textsubscript{eff} and H\textsubscript{rate}}
Initially, Kolmogorov-Smirnov (KS) Goodness-of-Fit and Shapiro-Wilks (SW) tests were used to determine if the assumption of normality could be held for the data set. The data used for the tests was the number faults found by each participant. The reason this data was chosen was that it directly correlates to the data used in H\textsubscript{eff} and H\textsubscript{rate}. The KS and SW tests both reported p-values < 0.05. See Table 1 for the p-values of the KS and SW tests. The critical value analysis for the KS and SW showed similar results and thus the null hypotheses of the data being normally distributed was rejected. See Table 2 for more information about the critical value results of the KS and SW tests.

>>>>

\SubSection{Tests Used for H\textsubscript{Eff} and H\textsubscript{Rate}}
Initially, Kolmogorov-Smirnov (KS) Goodness-of-Fit and Shapiro-Wilks (SW) tests were used to determine if the assumption of normality could be held for the data set. The data used for the tests was the number faults found by each participant. The reason this data was chosen was that it directly correlates to the data used in H\textsubscript{Eff} and H\textsubscript{Rate}. No data points were removed from the data set before performing any tests for H\textsubscript{Eff} or H\textsubscript{Rate}. The reasoning for this was that the hypotheses only concern number of occurances and not the qualitative attributes of the data. This means that data points which, for example, contained ``incorrect'' \textit{Item numbers} were still used in the calculation.

The KS and SW tests both reported p-values \textless 0.05. See Table 1 for the p-values of the KS and SW tests. The critical value analysis for the KS and SW showed similar results and thus the null hypotheses of the data being normally distributed was rejected. See Table 2 for more information about the critical value results of the KS and SW tests.
